---
title: "RProcess Module Functions"
subtitle: "R batch scripts from shiny session"
author: "Marc Schwering"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RProcess Module Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Contents

1. [Single R batch script](#single)  
2. [Multiple scripts](#multi)  


```{r setup, echo=FALSE, results="hide"}
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 7)
```

<br/><br/>



# Single R batch script<a name="single"></a>

blabla how it works
writing files, 1 for ifof, 1 for status
option to write log file
pid in case process is started before another finishes
convenience functions for use in R batch script

## Using `RProcess` <a name="single1"></a>

RProcess small example
shiny...



then process...

## Starting and polling Process seperately <a name="single2"></a>

Current directory with subdirectories `./tmp`, `./log`, `./scripts`. 
Btach R script in `./scripts` called `process.R` with:

```{r, eval = FALSE}
input <- shinyTools::Init(commandArgs(TRUE))

shinyTools::Log(c("Input is", input))
Sys.sleep(2)

if(input > 100) shinyTools::Abort("Input greater 100")

info <- shinyTools::Up(0.8)

Sys.sleep(4)
res <- shinyTools::Try(dpois(1:100, input))

shinyTools::Fin(res)
```

Then run app, which can run `Rscript ./scripts/process.R`.

```{r, eval=FALSE}
library(shinyTools)

check <- function(object, add){ if(object <= add$n) return(paste("Lambda must be greater", add$n, "idiot!"))}

ui <- fluidPage(sidebarLayout(
  sidebarPanel(
    h2("Distribution"),
    numericInput("num1", "set lambda", 10, -10, 50),
    RProcessStartUI("process"),
    actionButton("trigger", "Start"),
    helpText("Poisson distribution is created in R batch script with a few seconds delay."),
    br(),
    actionButton("num2", "check responsiveness"),
    verbatimTextOutput("num2"),
    helpText("By clicking on the button you can see that the app is still responsive while running the R batch script.")
  ),
  mainPanel(
    h3("Poisson Distribution"), 
    RProcessFinishUI("process"), 
    plotOutput("plot"), 
    h3("Return value of RProcessFinish"),
    verbatimTextOutput("result")
  )
))

server <-function(input, output, session) {
  callModule(RProcessStart, "process", trigger = reactive(input$trigger), object = reactive(input$num1),
             script = "./scripts/process.R", logFile = "log/log.log", pwd = "./tmp", sessionid = "asd",
             checkFun = "check", addArgs = list(n = 0))
  result <- callModule(RProcessFinish, "process", pwd = "./tmp")
  output$plot <- renderPlot(plot(1:100, result()$result))
  output$result <- renderPrint(result())
  output$num2 <- renderPrint(input$num2)
}

shinyApp(ui, server)
```

Same thing.

<br/><br/>

# Multiple scripts<a name="multi"></a>










